\documentclass[10pt]{article}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{indentfirst}
\usepackage{multicol}

\usepackage[margin=1in]{geometry}

\title{Dustin Alandzes}
\author{}
\date{}

\begin{document}
   \pagestyle{empty}
   \maketitle
   \thispagestyle{empty}

   \begin{center}
    \href{https://github.com/DustinAlandzes/}{https://github.com/DustinAlandzes/}
    \href{https://www.linkedin.com/in/dustinalandzes}{https://www.linkedin.com/in/dustinalandzes}
   \end{center}

   \section*{Work History}
   \textbf{\href{https://www.drchrono.com/}{DrChrono} (Remote)} \hfill {Februrary 2020 to November 2023}
   \begin{itemize}
     \item[] \textit{Software Engineer}
     \item[] Added features and fixed bugs using Python, Django, TypeScript and React.
     \item[] Implemented prior authorization which allows providers to ask a patient's insurance if they will pay for a prescription.
     \item[] Took ownership of the lab functionality, responded to incidents and had meetings with partners like Quest.
     \item[] Built two-factor authentication for prescribing controlled substances using ID.me.
     \item[] Implemented a workflow that allows pharmacies to request changes for a prescription.
    \end{itemize}

   \textbf{\href{https://bootcamp.utsa.edu/coding/}{UTSA Coding Bootcamp} (San Antonio)} \hfill {January 2020 to June 2020}
    \begin{itemize}
     \item[] \textit{Teaching Assistant}
     \item[] Helped students learn JavaScript, Node.js and React.
     \item[] Graded homework and gave feedback on projects.
    \end{itemize}

     \textbf{\href{https://www.legalist.com/}{Legalist} (Remote)} \hfill {April 2019 to September 2019}
    \begin{itemize}
     \item[] \textit{Junior Software Developer}
     \item[] Gathered data about new lawsuits using Python, Django and Selenium.
     \item[] Integrated with the 2Captcha API to solve captcha challenges.
    \end{itemize}


  \textbf{\href{https://thedreamers.us/}{Dreamers Inc.} (Remote)} \hfill {December 2017 to March 2019}
    \begin{itemize}
     \item[] \textit{Full Stack Web Developer}
     \item[] Built projects for clients using Python, Django and React.
    \end{itemize}

   \textbf{\href{https://n-compass.tv/}{N-Compass TV} (San Antonio)} \hfill {August 2014 to December 2017}
    \begin{itemize}
        \item[] \textit{System Administrator}
        \item[] Created web applications using Python and JavaScript to display news, weather and sports information in businesses.
        \item[] Installed software on Windows and Linux computers.
        \item[] Visited local businesses to install computers and displays used to display advertisements.
    \end{itemize}

   \textbf{\href{https://armandomontelongo.com/}{Armando Montelongo} (San Antonio)} \hfill {June 2014 to August 2014}
    \begin{itemize}
     \item[] \textit{Web Development Intern}
     \item[] Used PHP and JavaScript to build an event management project.
    \end{itemize}

   \section*{Education}
   \noindent

  \textbf{\href{https://www.credly.com/badges/d4012af6-1c9f-4ca8-aa2a-931c2c3c8e5b}{Hashicorp}} \hfill {November 2021 to November 2023}
   \begin{itemize}
     \item[] \textit{Certified Terraform Associate}
     \item[] Gained knowledge and experience with Infrastructure as Code using AWS, GCP and Azure.
     \item[] Utilized that knowledge and got practical experience making small changes and adding linting to continuous integration of the AWS Terraform configuration for an electronic health record.
    \end{itemize}

  \textbf{\href{https://www.utsa.edu/}{University of Texas at San Antonio}} \hfill {August 2014 to December 2017}
   \begin{itemize}
     \item[] \textit{Non-graduate}
     \item[] Took an intro to electrical engineering class.
     \item[] Board member of the UTSA eSports Association where I ran Super Smash Brothers Melee tournaments and helped with fundraising.
   \end{itemize}

  \textbf{\href{https://www.scuc.txed.net/ByronSteele}{Byron P. Steele II}} \hfill {August 2010 to May 2014}
   \begin{itemize}
     \item[] \textit{High School Diploma}
   \end{itemize}

  \section*{Skills}

   \begin{multicols}{2}
   \begin{itemize}
        \item[] Python \& Django
        \item[] JavaScript \& TypeScript
        \item[] React
        \item[] Git \& GitHub
        \item[] Docker
        \item[] AWS \& Terraform
        \item[] Agile Methodology
        \item[] Test-Driven Development
   \end{itemize}
   \end{multicols}

\end{document}
